---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DocToRLlama (DrLlama)

<!-- badges: start -->
<!-- badges: end -->

The goal of DrLlama is to provide documentation on undocumented R code, to improve the reading of code written by others (or by you a long time ago).

## Installation

You can install the development version of DrLlama from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("zanmat/DrLlama")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(DrLlama)

llm_use("ollama", "llama3.2:3b", seed = 100, temperature = 0)

doc_to_code("my_code.R", "light")

# The function doc_to_code will read the .R file and create a copy starting with "with_code_"

```

DrLlama requires having [Ollama](https://ollama.com/) installed and running.

